---
title: "Lambda Calculus"
author: "Jon Harmon"
date: "6/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Idiot

Take input and return it.

```{r Idiot}
I <- function(x) x
I(5) == 5
```

## Mockingbird

Take input and return that input called on itself.

```{r Mockingbird}
M <- function(f) f(f)
M(I)(5) == I(5)
```

## Kestrel

Take input and return a function that takes new input and returns the original input.

```{r Kestrel}
K <- function(c) function(i) c
identical(K(I)(2), I)
K(I)(2)(3) == 3
```

## Kite

Take input and return a function that ignores that input and returns its own input.

```{r Kite}
KI <- function(x) K(I)(x)
KI(2)(3) == 3
```

## Aside: Booleans

```{r redefine-bools}
T <- K
F <- KI
# Mess with the srcref so returning F shows FALSE and T shows TRUE
attr(T, "srcref") <- TRUE
attr(F, "srcref") <- FALSE
T
F
```

```{r not}
NOT <- function(p) p(F)(T)
NOT(T)
NOT(F)
```

```{r AND}
AND <- function(p) function(q) p(q)(p)
AND(F)(F)
AND(T)(T)
AND(F)(T)
AND(T)(F)
```

```{r OR}
OR <- function(p) function(q) p(p)(q)
OR(F)(F)
OR(F)(T)
OR(T)(F)
OR(T)(T)
```

OR is a special case of the mockingbird!
```{r mockingOR}
M(F)(F)
M(F)(T)
M(T)(F)
M(T)(T)
```

```{r EQUAL}
EQUAL <- function(p) function(q) p(q)(NOT(q))
EQUAL(T)(T)
EQUAL(T)(F)
EQUAL(F)(T)
EQUAL(F)(F)
```

## Cardinal

Take a 2-argument function and return that function but with its arguments reversed.
All of the sudden I need waaaay more complicated R code.
OH! Except the cardinal *is* NOT, so I can get closer.

```{r Cardinal}
C <- function(f) {
  function(a) function(b) f(b)(a)
}
```

This works for any function written in the same formal way, so, for example:

```{r testing}
testing <- function(a) function(b) paste(a, b)
testing(1)(2)
testing(2)(1)
C(testing)(1)(2) == testing(2)(1)
```

I'd like to test these equalities using `EQUAL`, but I need everything to be functions (and accept functions) for that to work, so... not yet.
